Leadership across cultures and contexts: an exploratory analysis

### 2020-04-26 leadership_across_cultures_contexts.Rmd
Added logisticPCA loading plots for k = 2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=F)
library(pander)
library(patchwork)
loadd(all_study_vars)
loadd(df_qual)
loadd(df_func)
loadd(plot_func_qual)
loadd(qualities_support_txt)
loadd(qualities_support_cult)
loadd(functions_support_txt)
loadd(functions_support_cult)
loadd(highstatus_plot)
loadd(plot_costs_benefits)
loadd(plot_pubdate)
source("R/cheapobjects.R")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=F)
library(pander)
library(patchwork)
loadd(all_study_vars)
loadd(df_qual)
loadd(df_func)
loadd(plot_func_qual)
loadd(qualities_support_txt)
loadd(qualities_support_cult)
loadd(functions_support_txt)
loadd(functions_support_cult)
loadd(highstatus_plot)
loadd(plot_costs_benefits)
loadd(plot_pubdate)
loadd(m_lpca_qual)
loadd(m_lpca_func)
source("R/cheapobjects.R")
```

@@

```{r logisticpcafunc, fig.height=8, fig.width=10, fig.cap="Logistic PCA of leader function variables with two principal components."}
logisticPCA_loadings_plot(m_lpca_func, df_func)
```

```{r logisticpcaqual, fig.height=10, fig.width=10, fig.cap="Logistic PCA of leader quality variables with two principal components."}
logisticPCA_loadings_plot(m_lpca_qual, df_qual)
```
